Detection of defects in additive manufacturing from a single x-ray projection using the empirical null filter

### 2019-08-09 reports/paper1/paper.tex
Adjust paper.tex

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/flowchart.eps}
  \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection.}
  \label{fig:flowchart}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/segment.JPG}
  \caption{The x-ray projection was segmented further into 7 segments or ROI.}
  \label{fig:inference_segmentFurther}
\end{figure}

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{X-ray projection with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{\pixel}$. a) X-ray projection with highlighted red positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/flowchart.pdf}
  \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection.}
  \label{fig:flowchart}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/segment.eps}
  \caption{The $z$ image was segmented further into 7 segments shown by the dotted red lines.}
  \label{fig:inference_segmentFurther}
\end{figure}

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=1.05\textwidth, height=4.9cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{X-ray projection with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{\pixel}$. a) X-ray projection with highlighted red positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}
